Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
lol

\section{Design}
In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser

@@

>>>>

\section{Design}
\#STORYTIMEE

In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser

@@

1) testing the pluggable transports
2) censorship environments
3) list of tasks
4) general design feedback (size, recruitment pool --ie general or journalists)
